The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update nobs fig cap

<!-- Figure: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for forage and open habitats. D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. Note, data in panel C are truncated because there were few observations of individuals in foraging and open habitats during the winter, resulting in inability to calculate layer similarity at lower number of observations.

>>>>

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased sharply for winter layers between ~10 - ~50 observations before stabilizing. Summer layers had consistent low layer relevance. C) Similarity of network layers across habitat classes and between seasons (e.g. open summer compared to open winter) was relatively consistent across number of observations for forest habitats. <!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers. D) Mean connective redundancy across individuals increased rapidly between ~10 - ~50 observations and then remained constant.
